### 2019-02-12 2-Chapters/3-Chapter/chapter3.tex
Still fighting against my template...

\begin{minted}[mathescape,
    linenos,
    numbersep=5pt,
    gobble=2,
    frame=lines,
    framesep=2mm]{csharp}
string title = "This is a Unicode π in the sky"
/*
Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
of an $n$-sided regular polygon circumscribing a
circle of diameter $d$.
*/
const double pi = 3.1415926535
\end{minted}

@@

% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}

@@

% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}

>>>>

\begin{listing}[H]
\begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python}
from SMPyBandits.Arms import Bernoulli
arms = [Bernoulli(0.1), Bernoulli(0.9)]

from SMPyBandits.Environment import MAB
my_MAB_problem = MAB(arms)
nbArms = my_MAB_problem.nbArms

from SMPyBandits.Policy import UCB
my_UCB_algo = UCB(nbArms, alpha=0.5)

horizon = 1000
for t in range(horizon):
    chosen_arm = my_UCB_algo.choice()
    observed_reward = my_MAB_problem.draw(chosen_arm)
    my_UCB_algo.getReward(chosen_arm, observed_reward)
...
\end{minted}
\caption{First example of code}
\label{lst:3:example}
\end{listing}

@@

\begin{listing}[H]
% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
\inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{Python}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
\caption{Small example of \texttt{main.py} file}
\label{lst:3:main}
\end{listing}

@@

\begin{listing}[H]
% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
\inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{Python}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
\caption{Small example of \texttt{configuration.py} file}
\label{lst:3:configuration}
\end{listing}

### 2019-02-12 4-Listofpublications/Listofpublications.tex
Ok for tex root
Still fighting against my template...

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix A ****************************
\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}

@@

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, par \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, avril 2019.
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, par \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Démonstration
  présentée à ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, juin 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, par \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Espagne, avril 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, par \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Espagne,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, par
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, septembre 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{prix
  du meilleur article}.
\end{etaremune}

@@

\section*{Other National Communications}
\renewcommand{\labelenumi}{[ONC-\arabic{enumi}]}
\begin{etaremune}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jul 2017
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, Mar 2017
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, Mar 2017
	\item	R. Bonnefoi, \textbf{L. Besson}, ``Multi-Armed Bandit Learning in IoT Networks'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jun 2016
\end{etaremune}

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
	\href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
	Bound for Channel Selection in LPWA Networks with Retransmissions},
	par \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
	Manco-Vasquez,
	\href{https://moychris.wordpress.com/}{C. Moy}. Septembre 2018.
\item
	\href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
	Open-Source Research Framework for Single and Multi-Players Multi-Arms
	Bandits (MAB) Algorithms in Python}, par \textbf{L. Besson},
	développement depuis octobre 2016 et encore actif,
	\href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code sur
	\href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
	(environ 40000 lignes), documentation sur
	\href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
\item
	\href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
	Can and Can't Do for Multi-Armed Bandits}, par \textbf{L. Besson} \&
	\href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
	Kaufmann}, septembre 2018,
	\href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
\item
	\href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
	Function and a Useful Sum-Inequality}, par \textbf{L. Besson}, février
	2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}

>>>>

%!TEX root = ../PhD_thesis__Lilian_Besson
% ******************************* Thesis Appendix A ****************************
\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}

@@

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, by \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019, \href{https://hal.inria.fr/hal-02006825}{HAL-02006825}.
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, by \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Demonstration
  presented at ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, June 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}, \href{https://hal.inria.fr/hal-02013866}{HAL-02013866}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Spain, April 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, by \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Spain,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, par
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, septembre 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{prix
  du meilleur article}.
\end{etaremune}

@@

\section*{Other National Communications}
\renewcommand{\labelenumi}{[ONC-\arabic{enumi}]}
\begin{etaremune}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jul 2017, \href{https://hal.inria.fr/hal-02013847}{HAL-02013847}
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, Mar 2017
	\item \textbf{L. Besson}, E. Kaufmann, ``Multi-Players Bandits Revisited'', in \emph{SCEE Seminar}, Rennes, France, Mar 2017
	\item	R. Bonnefoi, \textbf{L. Besson}, ``Multi-Armed Bandit Learning in IoT Networks'', in \emph{Journ\'{e}e Des Doctorants de l'IETR}, Rennes, France, Jun 2016, \href{https://hal.inria.fr/hal-02013839}{HAL-02013839}
\end{etaremune}

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
	\href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
	Bound for Channel Selection in LPWA Networks with Retransmissions},
	par \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
	Manco-Vasquez,
	\href{https://moychris.wordpress.com/}{C. Moy}. Septembre 2018.
\item
	\href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
	Open-Source Research Framework for Single and Multi-Players Multi-Arms
	Bandits (MAB) Algorithms in Python}, by \textbf{L. Besson},
	développement depuis octobre 2016 et encore actif,
	\href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code sur
	\href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
	(environ 40000 lignes), documentation sur
	\href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
\item
	\href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
	Can and Can't Do for Multi-Armed Bandits}, by \textbf{L. Besson} \&
	\href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
	Kaufmann}, septembre 2018,
	\href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
\item
	\href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
	Function and a Useful Sum-Inequality}, by \textbf{L. Besson}, février
	2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}

### 2019-02-12 Nomenclature/Nomenclature.tex
Still fighting against my template...

\nomenclature[A]{AM}{\textit{Amplitude Modulation}}
\nomenclature[A]{ARTM}{\textit{Advanced Range Telemetry Group}}
\nomenclature[A]{COFDM}{\textit{Coded Orthogonal Frequency Division Multiplexing}}
\nomenclature[A]{CPM}{\textit{Continuous Phase Modulation}}
\nomenclature[A]{CPFSK}{\textit{Continuous Phase Frequency Shift Keying}}
\nomenclature[A]{FM}{\textit{Frequency Modulation}}
\nomenclature[A]{PCM/FM}{\textit{Pulse Code Modulation/Frequency Modulation}}
\nomenclature[A]{MHz}{\textit{Megahertz}}
\nomenclature[A]{GHz}{\textit{Gigahertz}}
\nomenclature[A]{Hz}{\textit{Hertz}}
\nomenclature[A]{dB}{\textit{Decibel}}
\nomenclature[A]{NRZ}{\textit{Non-Return to Zero}}
\nomenclature[A]{SOQPSK}{\textit{Shaped Offset Quadrature Phase-Shift Keying}}
\nomenclature[A]{SOQPSK-TG}{\textit{Shaped Offset Quadrature Phase-Shift Keying Telemetry Group}}
\nomenclature[A]{SOQPSK-MIL}{\textit{Shaped Offset Quadrature Phase-Shift Keying Military}}
\nomenclature[A]{MIL-STD SOQPSK}{\textit{Military Standard Shaped Offset Quadrature Phase-Shift Keying }}
\nomenclature[A]{APSK}{\textit{Amplitude Phase-Shift Keying}}
\nomenclature[A]{PSK}{\textit{Phase-Shift Keying}}
\nomenclature[A]{M-PSK}{\textit{M-ary Phase-Shift Keying}}
\nomenclature[A]{BPSK}{\textit{Binary Phase-Shift Keying}}
\nomenclature[A]{OQPSK}{\textit{Offset Quadrature Phase-Shift Keying}}
\nomenclature[A]{PAM}{\textit{Pulse Amplitude Modulation}}
\nomenclature[A]{M-QAM}{\textit{M-ary Quadrature Amplitude Modulation}}
\nomenclature[A]{MIMO}{\textit{Multiple Input Multiple Output}}
\nomenclature[A]{SISO}{\textit{Single Input Single Output}}
\nomenclature[A]{MISO}{\textit{Multiple Input Single Output}}
\nomenclature[A]{RF}{\textit{Radio Frequency}}
\nomenclature[A]{IRIG}{\textit{Inter-Range Instrumentation Group}}
\nomenclature[A]{RCC}{\textit{Range Commanders Council}}
\nomenclature[A]{ISI}{\textit{Inter-Symbol Interference}}
\nomenclature[A]{PRD}{\textit{Perrins-Rice Decomposition}}
\nomenclature[A]{DBD}{\textit{DuoBinary Decomposition}}
\nomenclature[A]{XTCQM}{\textit{Cross-correlated Trellis Coded Modulation}}
\nomenclature[A]{I$\&$D}{\textit{Integrate and Dump}}
\nomenclature[A]{CM}{\textit{Constant Modulus}}
\nomenclature[A]{CMA}{\textit{Constant Modulus Algorithm}}
\nomenclature[A]{LOS}{\textit{Line Of Sight}}
\nomenclature[A]{NLOS}{\textit{Non-Line Of Sight}}
\nomenclature[A]{STC}{\textit{Space-Time Coding}}
\nomenclature[A]{STBC}{\textit{Space-Time Block Coding}}
\nomenclature[A]{PSP}{\textit{PerSurvivor Processing}}
\nomenclature[A]{GMSK}{\textit{Gaussian Minimum Shift Keying}}
\nomenclature[A]{MSK}{\textit{Minimum Shift Keying}}
\nomenclature[A]{LS}{\textit{Least Square}}
\nomenclature[A]{LMS}{\textit{Least Mean Square}}
\nomenclature[A]{RLS}{\textit{Recursive Least Square}}
\nomenclature[A]{GSM}{\textit{Global System for Mobile communication }}
\nomenclature[A]{BT}{\textit{Bandwidth Time product}}
\nomenclature[A]{GFSK}{\textit{Gaussian Frequency Shift Keying}}
\nomenclature[A]{SBPSK}{\textit{Shaped Binary Phase-Shift Keying}}
\nomenclature[A]{DVB-RCS2}{\textit{Digital Video Broadcasting - Return Channel via Satellite - Second Generation}}
\nomenclature[A]{FQPSK}{\textit{Feher-patented Quadrature Phase-Shift Keying}}
\nomenclature[A]{RC}{\textit{Raised Cosine}}
\nomenclature[A]{REC}{\textit{Rectangular}}
\nomenclature[A]{BCJR}{\textit{Bahl, Cocke, Jelinek and Raviv}}
\nomenclature[A]{MAP}{\textit{Maximum A Posteriori}}
\nomenclature[A]{MLSD}{\textit{Maximum Likelihood Sequence Detection}}
\nomenclature[A]{CA-MLSD}{\textit{Conventional Adaptive Maximum Likelihood Sequence Detection}}
\nomenclature[A]{NA-MLSD}{\textit{Non-Adaptive Maximum Likelihood Sequence Detection}}
\nomenclature[A]{MLSD}{\textit{Maximum Likelihood Sequence Detection}}
\nomenclature[A]{MLSE}{\textit{Maximum Likelihood Sequence Estimation}}
\nomenclature[A]{Mbps}{\textit{Megabits per second}}
\nomenclature[A]{MMSE}{\textit{Minimum Mean Square Error}}
\nomenclature[A]{MSE}{\textit{Mean Square Error}}
\nomenclature[A]{SMA}{\textit{Saint Martin Airport}}
\nomenclature[A]{TBA}{\textit{Toulouse-Blagnac Airport}}
\nomenclature[A]{V2V}{\textit{Vehicle To Vehicle}}
\nomenclature[A]{AWGN}{\textit{Additive White Gaussian Noise}}
\nomenclature[A]{SxS}{\textit{Sample by Sample}}
\nomenclature[A]{SNR}{\textit{Signal-to-Noise Ratio}}
\nomenclature[A]{SER}{\textit{Symbol Error Rate}}
\nomenclature[A]{BER}{\textit{Bit Error Rate}}
\nomenclature[A]{ASM}{\textit{Asynchronous Marker}}
\nomenclature[A]{INET}{\textit{Integrated Network Enhanced Telemetry}}
\nomenclature[A]{STBD}{\textit{Space-Time Block Decoder}}
\nomenclature[A]{ML}{\textit{Maximum Likelihood}}
\nomenclature[A]{ML-ASM}{\textit{Maximum Likelihood - Approximate Signal Model}}
\nomenclature[A]{OD}{\textit{Offset Decode}}
\nomenclature[A]{SOVA}{\textit{Soft Output Viterbi Algorithm}}
\nomenclature[A]{LLR}{\textit{Log-Likelihood Ratio}}
\nomenclature[A]{FIR}{\textit{Finite Impulse Response}}
\nomenclature[A]{Max-Log-MAP}{\textit{Maximum Logarithm Maximum A Posteriori}}
\nomenclature[A]{FEC}{\textit{Forward Error Correction}}
\nomenclature[A]{LDPC}{\textit{Low Parity Density Check}}
\nomenclature[A]{CFO}{\textit{Carrier Frequency Offset}}
\nomenclature[A]{US}{\textit{United States}}
\nomenclature[A]{DF}{\textit{Decision Feedback}}
\nomenclature[A]{I.I.D}{\textit{Independent and Identically Distributed}}
\nomenclature[A]{ML-ASM}{\textit{Maximum Likelihood - Approximate Signal Model}}
\nomenclature[A]{NASA's JPL}{\textit{National Aeronautics and Space Administration's Jet Propulsion Lab}}
%\nomenclature[N]{$x$}{Scalar}

>>>>

\nomenclature[A]{UCB}{\textit{Upper Confidence Bound} (object or algorithm)}
\nomenclature[A]{klUCB}{\textit{Kullback-Leibler Upper Confidence Bound} (algorithm)}
\nomenclature[A]{KL}{\textit{Kullback-Leibler} (divergence)}
\nomenclature[A]{MCTopM}{\textit{Musical-Chair on Top-M} (algorithm)}
\nomenclature[A]{RandTopM}{\textit{Random Hoping Musical-Chair on Top-M} (algorithm)}
\nomenclature[A]{GLR}{\textit{Generalized Likelihood Ratio}}
\nomenclature[A]{GLRT}{\textit{Generalized Likelihood Ratio Test}}
